---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# uncover

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental) [![R-CMD-check](https://github.com/Reckziegel/uncover/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Reckziegel/uncover/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

The goal of `uncover` is to help users to perform the second step in Meucci’s Checklist: __Estimation__.

## Installation

You can install the development version of `uncover` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Reckziegel/uncover")
```

## Usage

From __The Prayer__:

> "*...the estimation step is the process of fitting a distribution to both, the observed past realizations of the invariants, and (optionally) additional information that is available at the current time* $T$..."

In `uncover` the "market" distribution can be estimated from historical scenarios or through the analytical approach. 

This brief introduction presents both.

```{r, warning=FALSE, message=FALSE}
# set up
library(tidyverse)
library(uncover)
library(ffp)

set.seed(123)

# invariants
x <- as_tibble(diff(log(EuStockMarkets)))
x
```

## Analytical Solution

Start with `reveal` to figure out which distribution presents the "best" _in-sample_ fit according to the AIC criteria:

```{r}
reveal(x)
```

In the current sample, the asymmetric Generalized Hyperbolic Distribution (GHD) fits best. To model the GHP use `fit_ghp`:

```{r}
fit <- fit_ghd(x)
fit
```

The family of functions `fit_*()` is available for different distribution specifications, which include:

- `fit_ghd`: for the [generalized hyperbolic distribution](https://en.wikipedia.org/wiki/Generalised_hyperbolic_distribution)
- `fit_hyp`: for the [hyperbolic distribution](https://en.wikipedia.org/wiki/Hyperbolic_distribution)
- `fit_nig`: for the [generalized inverse gaussian distribution](https://en.wikipedia.org/wiki/Generalized_inverse_Gaussian_distribution#:~:text=In%20probability%20theory%20and%20statistics%2C%20the%20generalized%20inverse,b%20%3E%200%20and%20p%20a%20real%20parameter.)
- `fit_vg`: for the [variance gamma distribution](https://en.wikipedia.org/wiki/Variance-gamma_distribution#:~:text=The%20variance-gamma%20distribution%2C%20generalized%20Laplace%20distribution%20or%20Bessel,distribution%20decrease%20more%20slowly%20than%20the%20normal%20distribution.)
- `fit_t`: for the [student-t distribution](https://en.wikipedia.org/wiki/Student%27s_t-distribution)
- `fit_normal`: for the [normal distribution](https://en.wikipedia.org/wiki/Normal_distribution)

Once a target distribution is chosen, the randomness of the "market" can be simulated in a large panel with `simulate_margins`:

```{r}
dist <- simulate_margins(model = fit, n = 100000)
dist
```

## Historical Scenarios

Historical scenarios play nice with the [Fully Flexible Probabilities](https://reckziegel.github.io/FFP/). 
Bootstrapping can be done very quickly in this approach:

```{r}
# prior probabilities
p <- rep(1 / nrow(x), nrow(x))

boot <- bootstrap_scenarios(x = x, p = as_ffp(p), n = 100000)
boot
```

To "twick" the probability vector, use any of the functions avaiable in the [ffp](https://reckziegel.github.io/FFP/) package. 

Here, probabilities are modeled as an exponential decay, in order to give more importance to recent events:

```{r}
# Exponential Smoothing
probs <- exp_decay(x = x, lambda = 0.01)

boot_decay <- bootstrap_scenarios(x = x, p = probs, n = 100000)
boot_decay
```

For more details on flexible probabilities, please, refer to the [ffp](https://reckziegel.github.io/FFP/) package and the papers bellow:

- [Fully Flexible Views: Theory and Practice](https://papers.ssrn.com/sol3/papers.cfm?abstract_id=1213325)
- [Historical Scenarios with Fully Flexible Probabilities](https://papers.ssrn.com/sol3/papers.cfm?abstract_id=1696802) 

## Estimation Risk

From now on the "estimation risk" takes place which will have an impact on the entire Checklist. 

```{r, message=FALSE, warning=FALSE}
dist_tidy <- dist |> 
  pivot_longer(cols = everything()) |> 
  add_column(Type = "Analytical")
boot_tidy <- boot |> 
  pivot_longer(cols = everything()) |> 
  add_column(Type = "Historical")
exp_tidy <- boot_decay |> 
  pivot_longer(cols = everything()) |> 
  add_column(Type = "Historical FFP")

# plot
bind_rows(dist_tidy, boot_tidy, exp_tidy) |> 
  ggplot(aes(x = value, y = ..density.., color = Type, fill = Type)) + 
  geom_histogram(position = "identity", alpha = 0.5, bins = 100) + 
  facet_wrap(~name) + 
  scale_color_viridis_d(end = 0.75) + 
  scale_fill_viridis_d(end = 0.75) + 
  scale_x_continuous(labels = scales::percent_format(), limits = c(-0.05, 0.05)) +
  labs(x = NULL, y = NULL, color = NULL, fill = NULL) + 
  theme(legend.position = "bottom")
```

## Reference

- Meucci, Attilio, ‘The Prayer’ Ten-Step Checklist for Advanced Risk and Portfolio Management (February 2, 2011). Available at SSRN: https://ssrn.com/abstract=1753788 or http://dx.doi.org/10.2139/ssrn.1753788
